Hydra battles in Coq

### 2020-10-24 doc/hydras.tex
Corrections to Gamma0 (chapter and scripts)

\chapter{The ordinal \texorpdfstring{$\Gamma_0$}{Gamma0} first draft)}

\section{Introduction}
We present a notation system for the ordinal $\Gamma_0$, following Chapter V, Section 14 of~\cite{schutte}: ``A notation system fir the ordinals $<\Gamma_0$''.
We try to be as close as possible to Schütte's text and usual practices of \coq{} developments.

@@

\begin{Coqsrc}
Fixpoint plus (t1 t2 : T2) {struct t1}:T2 :=
  match t1,t2 with
  |  zero, y  => y
  |  x, zero => x
  |  gcons a b n c, gcons a' b' n' c' =>
     (match compare (gcons a b 0 zero)
                    (gcons a' b' 0 zero)
      with | Lt => gcons a' b' n' c'
      | Gt =>
        (gcons a b n
              (c +
               (gcons a' b' n' c')))
      | Eq  => (gcons a b (S(n+n')) c')
      end)
  end
where "alpha + beta" := (plus alpha beta): T2_scope.
\end{Coqsrc}

>>>>

\chapter{The ordinal \texorpdfstring{$\Gamma_0$}{Gamma0} (first draft)}

\emph{This chapter and the files it presents are still very incomplete, considering the impressive properties of $\Gamma_0$~\cite{Gallier91}.  We hope to add new material soon, and accept contributions!}

\section{Introduction}
We present a notation system for the ordinal $\Gamma_0$, following Chapter V, Section 14 of~\cite{schutte}: ``A notation system for the ordinals $<\Gamma_0$''.
We try to be as close as possible to Schütte's text and usual practices of \coq{} developments.

@@

\begin{Coqsrc}
Fixpoint plus (t1 t2 : T2) {struct t1}:T2 :=
  match t1,t2 with
  |  zero, y  => y
  |  x, zero => x
  |  gcons a b n c, gcons a' b' n' c' =>
     (match compare (gcons a b 0 zero)
                    (gcons a' b' 0 zero) with
      | Lt => gcons a' b' n' c'
      | Gt => gcons a b n (c + gcons a' b' n' c')
      | Eq => gcons a b (S(n+n')) c'
      end)
  end
where "alpha + beta" := (plus alpha beta): T2_scope.
\end{Coqsrc}
